Formal Paper Draft

### 2021-08-22 PaperDraft.Rmd
kmw

@@

>>>>

Overview of Penguin data.

Additionally, we simulated an additional penguin that stands out significantly from the additional penguins. The penguin is 5 standard deviations above or below the average for each of the measurements.

@@

```{r}
CC2015 <- read.csv("https://raw.githubusercontent.com/paulharmongj/Carnegie_SEM/master/data/CC2015data.csv")

CC2015_filter <- CC2015 %>% filter(BASIC2015 %in% c(15,16,17)) %>% select(PDNFRSTAFF, S.ER.D, NONS.ER.D, FACNUM, HUM_RSD, STEM_RSD, OTHER_RSD, SOCSC_RSD)
perplexity = 30

## NEED TO STANDARDIZE THE DATA FIRST (MAKE UNITLESS)
CCscale <- CC2015_filter %>% lapply(scale) %>% as_tibble()

out <- MultiPermanova(CCscale, maptype = "MDS")
```
